---
title: "Statistical Inference Final "
author: "Alejandro Borges Sanchez"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 80
---

```{r setup}
library(tidyverse)

```

# Overview:

I present a set of simulations to explore the difference between the exponential
distribution and the Central Limit Theorem.

We are asked to respect the lambda parameter for simulations. Since the main
parameter is $\lambda$ , $\mu=1/\lambda$ and $\sigma=1/\lambda$, we set:

$\lambda = 0.2$

```{r}
GLambda<-0.2
Gmu<-1/GLambda
Gsigma<-1/GLambda
```

# Simulations:

We are told that we will need to do $sims=1000$ simulations of averages of
exactly 40 exponential numbers, thus $n=40$. Aditionally, I will use a seed
$ourSeed=123$ for all simulations except and *if* some other seed is needed:

```{r}
sims<-1000
n<-40
ourSeed<-123
set.seed(ourSeed)
```

We begin by getting a dataframe 1000 rows long, each with the corresponding
simulation of 40 numbers from the exponential with rate=GLambda, as a list
column called simdata:

```{r}
simulations<-tibble(
    simnum=seq(1,sims)
)%>%
    mutate(
        simdata=purrr::map(.$simnum,~rexp(n=40,rate=GLambda))
    )  %>%
    mutate(
        single_mean=purrr::map_dbl(.$simdata,~mean(.x)),
        single_median=purrr::map_dbl(.$simdata,~median(.x))
    )
```

**simulations** is now a tibble with a list-column harboring 40 exponential
draws, with the rate set to GLambda.

We can get our references or "theoretical" distribution from the [wikipedia
page](https://en.wikipedia.org/wiki/Exponential_distribution) of the exponential
distribution:

> $$
> f(x; \lambda) = \begin{cases}    \lambda e^{- \lambda e} \text{ if } x \gtrsim 0\\
>     0 \text{ if } x \lt 0 
> \end{cases}
> $$
>
> Here *λ* \> 0 is the parameter of the distribution, often called the *rate
> parameter*. The distribution is supported on the interval [0, ∞). If a [random
> variable](https://en.wikipedia.org/wiki/Random_variable "Random variable") *X*
> has this distribution, we write *X* \~ Exp(*λ*).
>
> The exponential distribution exhibits [infinite
> divisibility](https://en.wikipedia.org/wiki/Infinite_divisibility_(probability) "Infinite divisibility (probability)").

Include English explanations of the simulations you ran, with the accompanying R
code. Your explanations should make clear what the R code accomplishes. \#Sample
Mean versus Theoretical Mean: Include figures with titles. In the figures,
highlight the means you are comparing. Include text that explains the figures
and what is shown on them, and provides appropriate numbers. \#Sample Variance
versus Theoretical Variance: Include figures (output from R) with titles.
Highlight the variances you are comparing. Include text that explains your
understanding of the differences of the variances. \#Distribution: Via figures
and text, explain how one can tell the distribution is approximately normal.
